Experimental Secure Multi-Party Computation on Real Data using SPDZ

### 2018-10-02 paper/nips_format.tex
Add files via upload

% ready for submission
%\usepackage{nips_2018}

% to compile a preprint version, e.g., for submission to arXiv, add
% add the [preprint] option:
 \usepackage[preprint]{nips_2018}

@@

\author{
  Valerie Chen\\
  Department of Computer Science\\
  Yale University\\
  %% Address?? \\
  \texttt{v.chen@yale.edu} \\
  %% examples of more authors
  \And
  Mariana Raykova \\
  Department of Computer Science\\
  Yale University \\
  %% Address?? \\
  \texttt{mariana.raykova@yale.edu} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

@@

In terms of an iterative approach to regression, [1] proposed a modification for the normalization in the iterative version of CGD that would be more stable with fixed-point numbers, which is detailed here:

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.45]{cgd_alg}
  \caption{Iterative fixed-point algorithm for CGD}
\end{figure}
We applied the same algorithm to SPDZ to see if the same modification would work. The goal of comparing iterative versus a direct method would be to justify the potential accuracy trade off for a much smaller run time.

@@

\subsubsection*{Acknowledgments}

Who to put here / how long should this be / does this count in page limit?

>>>>

% ready for submission
\usepackage{nips_2018}

% to compile a preprint version, e.g., for submission to arXiv, add
% add the [preprint] option:
 %\usepackage[preprint]{nips_2018}

@@

\author{
  Valerie Chen\\
  Yale University\\
  %% Address?? \\
  \texttt{v.chen@yale.edu} \\
  \And
  Valerio Pastro\\
  Yale University\\
  \textt{valerio.pastro@yale.edu}\\
  %% examples of more authors
  \And
  Mariana Raykova \\
  Yale University \\
  %% Address?? \\
  \texttt{mariana.raykova@yale.edu} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

@@

In terms of an iterative approach to regression, [1] proposed a modification for the normalization in the iterative version of CGD that would be more stable with fixed-point numbers.

We applied the same algorithm to SPDZ to see if the same modification would work. The goal of comparing iterative versus a direct method would be to justify the potential accuracy trade off for a much smaller run time.

@@
